Legacy Data Confounds Genomics Studies

### 2019-03-29 legacy.tex
update

To build a test statistic to represent the association across all populations simultaneously, we performed a simple logistic regression predicting genotype based on $Q$ with population as a covariate to account for population structure.

@@

\begin{table}[h]
\centering
\begin{tabular}{l  r r}
                      & {Repeat}  & {Non-Repeat}       \\ \hline
{SNP}  & 5,186 & 17,124 \\  
{INDEL} & 509 & 1,571 \\ \hline
\end{tabular}
\caption{Number of statistically significant variants per category. Variants that are flagged by the 1kGP nested repeat mask file were analyzed separately. SNPs and INDELs were also analyzed separately. The total number of 24,390 are statistically significantly associated to $Q$.}
\label{sigTable}
\end{table}

@@

 \hline
\end{tabular}
\caption{A list of recent publications that reported suspicious variants as close to or above the genome-wide significant threshold. The variants reaching genome wide significance have a star ( * ). Note : with a FDR ($\alpha = 0.01$) p-value adjustment, values of -$\log_{10} p > 2$ are deemed significant. }
\label{gwasTable}
\end{table}

>>>>

To build a test statistic to represent the association across all populations simultaneously, we performed a simple logistic regression predicting genotype based on $Q$ with the logistic factor analysis (LFA) as an offset to account for population structure \citep{song2015testing}.

@@

\begin{table}
\centering
\begin{tabular}{l  r r}
                      & {Repeat}  & {Non-Repeat}       \\ \hline
{SNP}  & 5,186 & 17,124 \\  
{INDEL} & 509 & 1,571 \\ \hline
\end{tabular}
\caption{Number of statistically significant variants per category. Variants that are flagged by the 1kGP nested repeat mask file were analyzed separately. SNPs and INDELs were also analyzed separately. The total number of 24,390 are statistically significantly associated to $Q$.}
\label{sigTable}
\end{table}

@@

 \hline
\end{tabular}
\caption{A list of recent publications that reported suspicious variants as close to or above the genome-wide significant threshold. The variants reaching genome wide significance have a star ( * ). Note : with a FDR ($\alpha = 0.01$) p-value adjustment, values of $ p > -\log_{10}(\alpha)$ are deemed statistically significant. }
\label{gwasTable}
\end{table}
